Case Study (McKenna)

### 2020-07-15 Cases/mrp/Case Study (McKenna) .Rmd
Inserted the stan models into the casestudy and began to explain them

BEFORE FITTING logit_hier.stan INCLUDE IT HERE AND EXPLAIN THE MODEL...

```{stan logit-hier, output.var="logit_hier", eval=FALSE}

@@

```{stan downes, output.var="downes", eval=FALSE}

@@

```{stan stan-mrp, output.var="stan_mrp", eval=FALSE}

>>>>

Our first model is a hierarchical logit model. A logit model is appropriate for our data because of the biniary outcome variable. The hierarchical model is group baised on the group assignments determined by the categorical variables in the data.

```{stan logit-hier, output.var="logit_hier", eval=FALSE}
data {
  int<lower=1> D;
  int<lower=0> N;
  int<lower=1> L;
  int<lower=0,upper=1> y[N];
  int<lower=1,upper=L> ll[N];
  matrix[N, D] x;
}

parameters {
  real mu[D];
  real<lower=0> sigma[D];
  vector[D] beta[L];
}

model {
  mu ~ normal(0, 100);
  sigma ~ normal(0, 5);
  for (l in 1:L) {
    beta[l] ~ normal(mu, sigma);
  }
  for (n in 1:N) {
    y[n] ~ bernoulli_logit((x[n,] * beta[ll[n]]));
  }
}
```

@@

```{stan downes, output.var="downes", eval=FALSE}
data {
  int<lower=0> n;                                       // Number of survey participants

  int<lower=0> n_age;                                 // These are the number of categories
  int<lower=0> n_eth;                                    // for each poststratification factor
  int<lower=0> n_income;                                  // in the final model
  int<lower=0> n_male;                                   
  int<lower=0> n_state;

  int<lower=0,upper=1> outcome[n];                      // observed outcome data, 1=Yes, 0=No

  int<lower=0,upper=n_age> age[n];                  // These are the variables containing
  int<lower=0,upper=n_eth> eth[n];                        // the observed data for each
  int<lower=0,upper=n_income> income[n];                    // poststratification factor in the 
  int<lower=0,upper=n_male> male[n];                      // final model
  int<lower=0,upper=n_state> state[n];      
 }
parameters {                                            // Model parameters to be estimated:
  real b0;                                              // "intercept"
  real a_age[n_age];                                // age varying coeffs (depart from linear fit)
  real a_eth[n_eth];                                      // remoteness class varying coeffs 
  real a_income[n_income];                                    // seifa ieo varying coeffs (depart linear fit)
  real a_male[n_male];                                // english fluency varying coeffs
  real a_state[n_state];                                  // occupation varying coeffs
  real<lower=0> sigma_age;                            // age var(sd) component
  real<lower=0> sigma_eth;                               // remoteness class var(sd) component
  real<lower=0> sigma_income;                              // seifa ieo var(sd) component
  real<lower=0> sigma_male;                            // english fluency var(sd) component
  real<lower=0> sigma_state;                             // occupation var(sd) component
}
transformed parameters {                                // Model specification is here
  vector[n] outcome_hat;
  for (i in 1:n) {
    outcome_hat[i] = b0 + a_age[age[i]] + a_eth[eth[i]] + a_income[income[i]] + a_male[male[i]] + a_state[state[i]];
  }
}
model {                                                 // Model distributions for varying coefficients
  b0 ~ cauchy(0,2.5);                                   // and prior distributions for unmodelled                            // Can modify Cauchy scale parameter
                                                        // Can also specify a uniform distribution here
  a_age ~ normal(0, sigma_age);                     // or by setting upper and lower limits for
  a_eth ~ normal(0, sigma_eth);                           // unmodelled parameters in the parameter step
  a_income ~ normal(0, sigma_income);                         // above  
  a_male ~ normal(0, sigma_male);                      
  a_state ~ normal(0, sigma_state);

  sigma_age ~ cauchy(0,2.5);
  sigma_eth ~ cauchy(0,2.5);
  sigma_income ~ cauchy(0,2.5);
  sigma_male ~ cauchy(0,2.5);
  sigma_state ~ cauchy(0,2.5);

  outcome ~ bernoulli_logit(outcome_hat);               // For a continuous outcome, specify a
                                                        // normal distribution with an additional
                                                        // variance component, i.e.
                                                        // outcome ~ normal(outcome_hat, sigma_outcome)
                                                        // Note the prior distributions for 
                                                        // unmodelled parameters will change.
}
```

@@

```{stan stan-mrp, output.var="stan_mrp", eval=FALSE}
data {
  int<lower = 0> N;
  int<lower = 1, upper = 7> age[N];
  int<lower = 1, upper = 3> income[N];
  int<lower = 1, upper = 3> eth[N];
  int<lower = 1, upper = 2> male[N];
  int<lower = 1, upper = 50> state[N];
  int<lower = 0> y[N];
  int<lower = 0> P[7, 3, 3, 2, 50];
}
parameters {
  real alpha;
  real epsilon;
  real<lower = 0> sigma_beta;
  real<lower = 0> sigma_gamma;
  real<lower = 0> sigma_delta;
  real<lower = 0> sigma_rho;
  vector<multiplier = sigma_beta>[7] beta;
  vector<multiplier = sigma_gamma>[3] gamma;
  vector<multiplier = sigma_delta>[3] delta;
  vector<multiplier = sigma_rho>[50] rho;
}
model {
  y ~ bernoulli_logit(alpha + beta[age] + gamma[income] + delta[eth] + {epsilon, -epsilon}[male] + rho[state]);
  alpha ~ normal(0, 2);
  epsilon ~ normal(0, 2);
  sigma_beta ~ normal(0, 1);
  sigma_gamma  ~ normal(0, 1);
  sigma_delta ~ normal(0, 1);
  sigma_rho ~ normal(0, 1);
  beta ~ normal(0, sigma_beta);
  gamma ~ normal(0, sigma_gamma);
  delta ~ normal(0, sigma_delta);
  rho ~ norma(0, sigma_rho);
}
generated quantities {
  real expect_pos = 0;
  int total = 0;
  for (b in 1:7)
    for (c in 1:3)
      for (d in 1:3)
        for (f in 1:2)
          for (g in 1:50){
        total += P[b, c, d, f, g];
        expect_pos
          += P[b, c, d, f, g]
             * inv_logit(alpha + beta[b] + gamma[c] + delta[d] + {epsilon, -epsilon}[f] + rho[g]);
      }
  real<lower = 0, upper = 1> phi = expect_pos / total;
}
